---
title: "`r params$project_name`"
output: html_document
params:
  # project_name: "Raised platform on street"
  # project_key: "raised-platform-on-street"
  project_name: "3 Story Multi-family behind Staples above enclosed parking garage"
  project_key: "3-story-multi-family-behind-staples-above-enclosed-parking-garage"
  #project_name: "Nice potted plants on street"
  #project_key: "project_nice-potted-plants-on-street"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
```

```{r}
source("functions.R")

# params <- list(
#   project_name = "3 Story Multi-family behind Staples above enclosed parking garage",
#   project_key = "3-story-multi-family-behind-staples-above-enclosed-parking-garage")

p <- read_csv(projects_csv) %>% 
  filter(project_key == params$project_key)
```

# {.tabset}

## Overview

`r fld2str("Description")`

`r fld2str("Type of Vision")`

`r fld2str("Design Standards Affected")`

`r fld2str("If this proposal requires additional amendments to the downtown development standards, please justify those changes below.", "Design standards justification for amendment(s)")`

`r fld2str("Specific Address (if applicable)", "Specific Address")`

`r fld2str("Existing Land Use")`

`r fld2str("Proposed Land Use")`

```{r}
d <- read_csv(files_csv) %>% 
  filter(
    project_key == params$project_key,
    file_category == "image_overview")

if (nrow(d) == 1)
  include_graphics(d$path)
```

## Drawings

```{r, results='asis'}
read_csv(files_csv) %>% 
  filter(
    project_key == params$project_key,
    file_category == "image_overview") %>% 
  mutate(
    li_md = glue("* [{fname}]({path})")) %>% 
  pull(li_md)
```

## Images

```{r}
library(bsplus)

paths <- read_csv(files_csv) %>% 
  filter(
    project_key == params$project_key,
    file_category == "images") %>% 
  pull(path)

paths2carousel(paths)
```

## Sustainability

`r fld2str("Cost Range")`

`r fld2str("Time frame for societal ROI")`

`r fld2str("What kinds of multi-benefit, performance driven improvements would result from this project, with respect to resource management, energy efficiency, life cycle costs, avoided costs, etc?", "Mult-benefits")`

`r fld2str("What specific ecosystem services will be created, expanded or supported as a result of this project?", "Ecosystem services")`

